\subsection{Pros of flexible coils}
Flexible PCBs (Printed Circuit Boards) offer several advantages over traditional rigid PCBs. Here are some of the key pros of flexible PCBs:

\begin{enumerate}
    \item \textbf{Flexibility and Space Savings}: Flexible PCBs can bend and twist, allowing for compact and efficient use of space in electronic devices.
    
    \item \textbf{Lightweight}: The materials used in flexible PCBs are lightweight, making them ideal for applications where weight is a concern, such as in aerospace or portable electronics.
    
    \item \textbf{Improved Design Freedom}: Flex PCBs allow for more creative and versatile designs because they can be formed into complex shapes and fit into tight or irregular spaces.
    
    \item \textbf{Reduced Connectors and Interconnects}: Because flexible PCBs can bend, they can often eliminate the need for additional connectors and interconnects, reducing overall system complexity.
    
    \item \textbf{Vibration and Shock Resistance}: Flexible PCBs can absorb shock and vibrations better than rigid PCBs, making them suitable for use in environments where these are concerns.

    \item \textbf{Simplified Assembly}: With fewer connectors and interconnects, assembly becomes easier and faster, reducing labor and potential points of failure.
    
    \item \textbf{High-Density Interconnects}: Flexible PCBs can support fine-pitch components and high-density interconnects, making them suitable for advanced electronics.
\end{enumerate}